Fixing Vulnerabilities Hinders Maintainability (REG)

### 2019-05-23 paper/issre19.tex

@@

\begin{abstract}
Security is a requirement of utmost importance to produce software of high
quality. However, there is still a considerable amount of zero-day
vulnerabilities being discovered, and fixed, almost weekly. We suspect that 
when developers address these vulnerabilities on their code bases, they actually
affect the maintainability and, pottentially, the reliability of software through the
introduction of other vulnerabilities. This paper evaluates the impact 
of refactorings to improve security on the maintainability of open-source software. 
Maintainability is measured based on the \emph{Better Code Hub}'s model of 10 guidelines 
using a dataset including 607 security commits. Results show that fixing software
vulnerabilities hinders the maintainability of open-source software. This is,
particularly, the case for refactorings that address \emph{Broken Authentication
and Session Management} issues, \emph{Memory Leaks} and \emph{Denial-of-Service}
attacks. Furthermore, we conclude that changes to code bases to fix vulnerabilities
need to be performed with extra care in open-source software.
\end{abstract}

@@

Software quality is important because it is ultimately related to the overall
cost of developing, extending and maintaining software applications~\cite{slaughter1998evaluating}. 
Software quality characteristics include, but are not limited to functional correctnes,
reliability, usability, maintainability, and security~\cite{iso:2011}. Security is an 
important non-functional requirement during the development of software systems. 
However, there is still a considerable amount of zero-day vulnerabilities being
discovered, and fixed, almost weekly as disclosed by the Zero Day Initiative
website\footnote{Zero Day Initiative website available at
\url{https://www.zerodayinitiative.com/advisories/published/} (Accessed on \today{})}.
These vulnerabilities are gateways for attackers to penetrate systems and 
exploit their resources. As an example, in the last week of January $2019$, 
a severe vulnerability in Apple FaceTime was revealed\footnote{FaceTime vulnerability 
details available at \url{https://thehackernews.com/2019/01/apple-facetime-
privacy-hack.html} (Accessed on \today{})} --- the outcome of a design/logical
flaw that allowed callers to see and hear others without them picking up the call.

In $2011$, the International Organization for Standardization (ISO) issued an
update for software product quality ISO/IEC 25010~\cite{iso:2011} considering
\emph{Security} as one of the main software product quality characteristics. 
Unmaintainable code is hard to test, analyze and re-use, and thus more difficult
to find vulnerabilities and defects. Therefore, writing maintainable code
supports the production of more reliable software preventing the introduction of 
faults/vulnerabilities in the code bases\Sof{cite smth}. ISO describes software 
maintainability as ``the degree of effectiveness and
efficiency with which a software product or system can be modified to improve
it, correct it or adapt it to changes in environment, and in requirements'' on
software quality ISO/IEC 25010. Software maintainbility can also be defined as 
the property of software that reveals how easily the software system can be 
maintained~\cite{IEEEComputerSociety:2014:GSE:2616205} or recover after a failure.

@@

There is still little information about the impact of patching vulnerabilities
in open-source software maintainability. \textit{Are developers affecting software
maintainability when trying to improve software security?}, it is what we want to 
investigate. Our suspiciousness is that some of the patches may have a negative 
impact on the software maintainability and possibly even be the cause of the 
introduction of new vulnerabilities $-$ harming software reliability. Therefore, 
in this paper we present an empirical study on the evolution of patches of 
vulnerabilities accross open-source software.

As ISO does not provide any specific guidelines or formula to calculate 
maintainability, we resort on Software Improvement Group (SIG)'s web-based source 
code analysis service Better Code Hub (BCH) to compute the software compliance 
with a set of $10$ guidelines to produce quality software~\cite{Visser:2016:OREILLY} 
based in ISO/IEC 25010. The results obtained for each guideline are merged into a 
mathematical formula that calculates software maintainability. From a methodological 
perspective, we leveraged a dataset of $607$ security changes collected from open-source 
software. Each change provides two different versions of the software - the vulnerable 
one and the patched one. For each version, we calculate software maintainability, using 
the proposed formula, after BCH computes the compliance with each guideline. Thus, we 
assess the impact of security changes comparing the maintainbility value of both versions. 
We also compare the impact of security changes with regular changes on software
maintainability. For that, we also collect a dataset of regular changes and do the same 
experiments as for security changes. This empirical study exhibits proof that changes 
applied in the code bases to fix vulnerabilities affect code maintainability. 
Especially, for refactorings that address \emph{Broken Authentication and Session Management} 
issues, \emph{Memory Leaks} and \emph{Denial-of-Service} attacks. With this study, 
we intend to highlight the need for tools to predict the impact of patches on 
maintainability~\cite{4724577} and documentation to help developers adopt security 
best practices~\cite{6311252, 7927935, MESQUIDA201519}.

@@

% There are other well-known standards and models that have been proposed
% to increase software security: Common Criteria~\cite{common:2009} which received
% negative criticism regarding the costs associated and poor technical evaluation;
% the OWASP Application Security Verification Criteria~\cite{oswap:2009} which is
% focused only on web applications, and a model proposed by Xu et al. ($2013$)
% ~\cite{6616351} for rating software security (arguably, it was one of the
% first steps taken by SIG to introduce security on their maintainability model).

@@

This paper is structured as follows: section~\ref{sec:motivation} introduces an
example of a security refactoring of a known vulnerability found in
OpenSSL\footnote{Repository available at \url{https://github.com/openssl/openssl}
(Accessed on \today{})}; section~\ref{sec:methodology} describes the
methodology used to answer the research questions; section~\ref{sec:results}
presents the results and section~\ref{sec:discussion} discusses their
implications; section~\ref{sec:threats}, enumerates the threats to the validity of
this study; section~\ref{sec:rw} describes the different work and existing
literature in the field of study; and, finally, section~\ref{sec:conclusions}
concludes the main findings and elaborates on future work.
%
\section{Motivation and Research Questions}\label{sec:motivation}
%
Due to time-to-market pressure and the lack of security expertise, code-related
security flaws are generally detected \textit{after the fact}, i.e., when
hackers exploit them. It turns out that fixing these issues is as simple as
modifying the software code base. However, these refactorings may have a
negative impact on software maintenance --- e.g., developers might follow the
quickest solution to fix the problem and not necessarily the most elegant and
performant one. Thus, we want to understand how security refactorings impact
the maintainability of software.

As an example, consider the refactoring of the Datagram Transport Layer Security
(DTLS) protocol implementation in OpenSSL\footnote{OpenSSL is a toolkit that
contains open-source implementations of the SSL and TLS cryptographic
protocols.} to address a vulnerability where an attacker could cause a Denial-of-Service
(DoS) attack by crafting DTLS handshake messages to trigger memory allocations
corresponding to large length values. This vulnerability is listed at the Common
Vulnerabilities and Exposures dictionary as CVE-$2014$-$3506$\footnote{CVE-$2014$-$3506$
details available at \url{http://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2014-3506}
(Accessed on \today{})}. It is amongst the vulnerabilities studied in our
evaluation. The snippet in Listing~\ref{lst:vuln} presents the changes performed on the
\emph{ssl/d1\_both.c} file\footnote{CVE-$2014$-$3506$ fix available  at
\url{https://github.com/openssl/openssl/commit/1250f12613b61758675848f6600ebd914ccd7636}
(Accessed on \today{})} by the OpenSSL developers to patch the vulnerability.

Every SSL/TLS connection begins with a handshake which is responsible by the
negotiation between the two parties. DTLS provides a mechanism for fragmenting
a handshake message over a number of packets, each of which can be transmitted
separately over the internet from one party to another. The problem in
CVE-$2014$-$3506$ is that the size of the handshake message collected by the
receiver is not verified against the maximum size allowed by DTLS. It is then
allocated to a new fragment (cf. Listing~\ref{lst:vuln}, line~37). Thus, if an
attacker has access to one of these packages, the attacker can change the
handshake message size and trigger unnecessary memory allocations of large
length which can lead to memory exhaustion that could end in a DoS attack.

@@

The code changes performed to fix the vulnerability were the following:

~\ref{lst:func1} \texttt{dtls1\_max\_handshake\_message\_len} function was
inserted to return the maximum number of bytes allowed in a DTLS
handshake message for \texttt{s}. The minimum is $16$KB but it might be greater if
the maximum certificate list size (\texttt{s-$>$max\_cert\_list}) requires it. More
specifically, it checks if the maximum certificate list size requires more length 
than the maximum length (\texttt{max\_len}). If that condition holds, the function 
returns the size of the certificate list, otherwise, it returns the maximum length. 
This function replaces lines $18$--$21$.

@@

Although checking the maximum size of a handshake message seems an elementary
problem to repair, the example shows that there was a significant amount of
changes performed in the code base which produced a negative impact in the
maintainability. Even though the developer tries to simplify the
code base by introducing a smaller unit
\texttt{dtls1\_max\_handshake\_message\_len} (\ref{lst:func1}), this change also
disrupts two of the guidelines proposed by the Software Improvement Group (SIG) for
building maintainable software~\cite{Visser:2016:OREILLY}. It adds a new branch
point to the \texttt{dtls1\_process\_out\_of\_seq\_message} unit
(\ref{lst:func5}) increasing the cyclomatic complexity and breaking the
\emph{Write Simple Units of Code} guideline. Moreover, it increases the code base
size in $4$ lines of code ($13$ lines added, $9$ lines deleted) which
contributes to a potential violation of the \emph{Keep Your code base Small}
guideline. Hence, we have observed that the impact of this refactoring on the
OpenSSL maintainability was negative.

@@

\begin{framed}
\textit{\textbf{RQ1} What is the impact of security refactorings on the
maintainability of open-source software?}
\vspace{-0.1cm}
\end{framed}
\vspace{-0.2cm}

@@

\begin{framed}
\textit{\textbf{RQ2} Which patterns of security refactorings are more likely to
affect open-source software maintainability?}
\vspace{-0.1cm}
\end{framed}
\vspace{-0.2cm}
% here
There are security flaws that are more difficult to refactor than others. For
instance, implementing secure authentication is not as easy as fixing a
cross-site scripting vulnerability since usually the last one can be fixed
without adding new lines of code. A typical fix for the cross-site scripting
vulnerability is presented in Listing~\ref{lst:fix}. The developer added the
function \texttt{htmlentities} to \textit{escape} the data given by the variable
\texttt{\$\_['file']}. Knowing which patterns are more likely to increase
maintainability issues is one step forward to bring awareness to security
engineers of what patterns need more attention. The taxonomy of security
patterns used to answer this question is the same as the one provided by the
authors of the dataset~\cite{Reis:2017:IJSSE}. Maintainability is measured
separately for each pattern.

@@

\begin{framed}
\textit{\textbf{RQ1} What is the impact of security refactorings on the
maintainability of open-source software?}
\vspace{-0.1cm}
\end{framed}
\vspace{-0.2cm}

@@

\begin{framed}
\textit{\textbf{RQ2} Which patterns of security refactorings are more likely to
affect open-source software maintainability?}
\vspace{-0.1cm}
\end{framed}
\vspace{-0.2cm}

@@

\begin{framed}
\textit{\textbf{RQ2} Which patterns of security refactorings are more likely to
affect open-source software maintainability?}
\vspace{-0.1cm}
\end{framed}
\vspace{-0.2cm}

@@

The security refactorings dataset provided by the previous
work~\cite{Reis:2017:IJSSE} was collected based on the messages of GitHub
commits produced by project developers to classify the changes performed by them
to fix security flaws. This approach discards security refactorings that were
not explicit in commits messages.

Baseline commits are retrieved randomly by selecting one commit from the same
project of a given security refactoring. This approach softens the differences
that may result from the characteristics of each project. However,
maintainability may still be affected by the developers' experience, coding
style and software contribution policies which is not evaluated in this study.
Furthermore, this evaluation considers that $607$ regular commits are enough to
alleviate random irregularities in the maintainability differences of the
baseline.

@@

Researchers investigated the relationship between design patterns and software
maintainability~\cite{10.1007/978-3-642-35267-6-18}. $300$ revisions of
\texttt{JHotDraw} were analyzed to conclude that every introduced pattern
instance improved software maintainability. However, other studies show that the
use of design patterns may introduce maintainability issues into
software~\cite{4493325}. The present work studies how security patterns
influence maintainability for open-source software.

@@

\noindent
We thank the Software Improvement Group (SIG) team for all the support and
help in validating the methodology.
%ack pedro adao when accepted.

\balance

>>>>

\makeatletter
\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark}
\makeatother

@@

\begin{abstract}
Security is a requirement of utmost importance to produce software of high
quality. However, there is still a considerable amount of zero-day
vulnerabilities being discovered and fixed, almost weekly. We suspect that 
when developers address these vulnerabilities on their code bases, they actually
affect the maintainability and, potentially, the reliability of software through the
introduction of new vulnerabilities. This paper evaluates the impact 
of refactorings to improve security on the maintainability of open-source software. 
Maintainability is measured based on the \emph{Better Code Hub}'s model of 10 guidelines 
using a dataset including 607 security commits. Results show that fixing software
vulnerabilities hinders the maintainability of open-source software. This is,
particularly, the case for refactorings that address \emph{Broken Authentication
and Session Management} issues, \emph{Memory Leaks} and \emph{Denial-of-Service}
attacks. Furthermore, we conclude that changes to code bases to fix vulnerabilities
need to be performed with extra care in open-source software.
\end{abstract}

@@

Software quality is important because it is ultimately related to the overall
cost of developing, extending and maintaining software applications~\cite{slaughter1998evaluating}. 
Software quality characteristics include, but are not limited to functional correctnes,
reliability, usability, maintainability, and security. Security is an 
important non-functional requirement during the development of software systems. 
However, there is still a considerable amount of zero-day vulnerabilities being
discovered, and fixed, almost weekly as disclosed by the Zero Day Initiative
website\footnote{Zero Day Initiative website available at
\url{https://www.zerodayinitiative.com/advisories/published/} (Accessed on \today{})}.
These vulnerabilities are gateways for attackers to penetrate systems and 
exploit their resources. As an example, in the last week of January $2019$, 
a severe vulnerability in Apple FaceTime was revealed\footnote{FaceTime vulnerability 
details available at \url{https://thehackernews.com/2019/01/apple-facetime-
privacy-hack.html} (Accessed on \today{})} --- the outcome of a design/logical
flaw that allowed callers to see and hear others without them picking up the call.

In $2011$, the International Organization for Standardization (ISO) issued an
update for software product quality ISO/IEC 25010 considering
\emph{Security} as one of the main software product quality characteristics~\cite{iso:2011}. 
However, many developers still lack the knowledge about best practices to deliver secure and high-quality software~\cite{Pothamsetty:2005:SEL:1107622.1107635, 8077802}.
Unmaintainable code is hard to test, analyze and re-use, and thus more difficult
to find vulnerabilities and defects. Therefore, writing maintainable code
supports the production of more reliable software preventing the introduction of 
faults/vulnerabilities in the code bases. ISO describes software 
maintainability as ``the degree of effectiveness and
efficiency with which a software product or system can be modified to improve
it, correct it or adapt it to changes in environment, and in requirements'' on
software quality ISO/IEC 25010~\cite{iso:2011}. Novel tools have been built to 
detect automatically software vulnerabilities (e.g., FindBugs, Infer and more). 
Despite these efforts, improving software security is not a trivial task and requires 
implementing refactorings that might affect software maintainability. 
Our suspiciousness is that some of the these patches may have a negative 
impact on the software maintainability and, possibly, even be the cause of the 
introduction of new vulnerabilities $-$ harming software reliability. Therefore, 
in this paper, we present an empirical study on the impact of patches of 
vulnerabilities in software maintenance accross open-source software.

% Software maintainability can also be defined as 
% the property of software that reveals how easily the software system can be 
% maintained~\cite{IEEEComputerSociety:2014:GSE:2616205} or recover after a failure.

@@

% There is still little information about the impact of patching vulnerabilities
% in open-source software maintainability. \textit{Are developers affecting software
% maintainability when trying to improve software security?}, it is what we want to
% investigate.

As ISO does not provide any specific guidelines or formulas to calculate 
maintainability, we resort on Software Improvement Group (SIG)'s web-based source 
code analysis service Better Code Hub (BCH) to compute the software compliance 
with a set of $10$ guidelines/metrics to produce quality software 
based in ISO/IEC 25010~\cite{Visser:2016:OREILLY}. The code metrics used by BCH 
were empirically validated in previous work~\cite{Bijlsma:2012:FIR:2317098.2317124, 8530041}. 
There are other well-known standards and models that have been proposed
to increase software security: Common Criteria~\cite{common:2009} which received
negative criticism regarding the costs associated and poor technical evaluation;
the OWASP Application Security Verification Criteria~\cite{oswap:2009} which is
focused only on web applications, and a model proposed by Xu et al. ($2013$)
~\cite{6616351} for rating software security (arguably, it was one of the
first steps taken by SIG to introduce security on their maintainability model). 
We use BCH's toolset to provide an assessment of maintainability in 
software mainly due to the broad number of metrics used.

From a methodological 
perspective, we leveraged a dataset of $607$ security refactorings collected from open-source 
software. We calculate software maintainability before and after the refactoring to measure its 
impact. This empirical study exhibits proof that changes 
applied in the code bases to fix vulnerabilities affect code maintainability. 
Especially, for refactorings that address \emph{Broken Authentication and Session Management} 
issues, \emph{Memory Leaks} and \emph{Denial-of-Service} attacks. This is important work
because there is still little information about the impact of security patches on the software
maintainability. With this study, 
we intend to highlight the need for tools to predict the impact of patches on 
maintainability~\cite{4724577} and documentation to help developers adopt security 
best practices~\cite{6311252, 7927935, MESQUIDA201519}.

@@

@@

This paper is structured as follows: section~\ref{sec:motivation} introduces an
example of a security refactoring of a known vulnerability found in
OpenSSL\footnote{\label{openssl}OpenSSL is a toolkit that
contains open-source implementations of the SSL and TLS cryptographic
protocols. Repository available at \url{https://github.com/openssl/openssl}
(Accessed on \today{})}; section~\ref{sec:methodology} describes the
methodology used to answer the research questions; section~\ref{sec:results}
presents the results and section~\ref{sec:discussion} discusses their
implications; section~\ref{sec:threats}, enumerates the threats to the validity of
this study; section~\ref{sec:rw} describes the different work and existing
literature in the field of study; and, finally, section~\ref{sec:conclusions}
concludes the main findings and elaborates on future work.
%
\section{Motivation and Research Questions}\label{sec:motivation}
%
Due to time-to-market pressure and the lack of security expertise~\cite{8077802}, code-related
security flaws are generally detected \textit{after the fact}, i.e., when
hackers exploit them. It turns out that fixing these issues is as simple as
modifying the software code base. However, these refactorings may have a
negative impact on software maintenance --- e.g., developers might follow the
quickest solution to fix the problem and not necessarily the most elegant and
performant one. Thus, we want to understand how security refactorings impact
the maintainability of software.

As an example, consider the refactoring of the Datagram Transport Layer Security
(DTLS) protocol implementation in OpenSSL\footnoteref{openssl} to address a vulnerability where an attacker could cause a Denial-of-Service
(DoS) attack by crafting DTLS handshake messages to trigger memory allocations
corresponding to large length values. This vulnerability is listed at the Common
Vulnerabilities and Exposures dictionary as CVE-$2014$-$3506$\footnote{CVE-$2014$-$3506$
details available at \url{http://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2014-3506}
(Accessed on \today{})}. It is amongst the vulnerabilities studied in our
evaluation. The snippet, in Listing~\ref{lst:vuln}, presents the changes performed on the
\emph{ssl/d1\_both.c} file\footnote{CVE-$2014$-$3506$ fix available  at
\url{https://github.com/openssl/openssl/commit/1250f12613b61758675848f6600ebd914ccd7636}
(Accessed on \today{})} by the OpenSSL developers to patch the vulnerability. Every SSL/TLS connection begins with a handshake which is responsible by the
negotiation between the two parties. DTLS provides a mechanism for fragmenting
a handshake message over a number of packets, each of which can be transmitted
separately over the internet from one party to another. The problem in
CVE-$2014$-$3506$ is that the size of the handshake message collected by the
receiver is not verified against the maximum size allowed by DTLS. It is then
allocated to a new fragment (cf. Listing~\ref{lst:vuln}, line~36). Thus, if an
attacker has access to one of these packages, he can change the
handshake message size and trigger unnecessary memory allocations of large
length which can lead to memory exhaustion that could end in a DoS attack.

@@

The code changes performed to fix the vulnerability are:

~\ref{lst:func1} \texttt{dtls1\_max\_handshake\_message\_len} function was
inserted to return the maximum number of bytes allowed in a DTLS
handshake message for \texttt{s}. The minimum is $16$KB but it might be greater if
the maximum certificate list size (\texttt{s-$>$max\_cert\_list}) requires it. More
specifically, it checks if the maximum certificate list size requires more length 
than the maximum length (\texttt{max\_len}). If that condition holds, the function 
returns the size of the certificate list, otherwise, it returns the maximum length. 
This function replaces lines $17$--$21$.

@@

Although checking the maximum size of a handshake message seems an elementary
problem to repair, the example shows that there was a significant amount of
changes performed in the code base which produced a negative impact in the
maintainability. Even though the developer tries to simplify the
code base by introducing a smaller unit
\texttt{dtls1\_max\_handshake\_message\_len} (\ref{lst:func1}), this change disrupts
one of the guidelines proposed by the Software Improvement Group (SIG) for
building maintainable software~\cite{Visser:2016:OREILLY}. It adds a new branch
point to the \texttt{dtls1\_process\_out\_of\_seq\_message} unit
(\ref{lst:func5}) increasing the cyclomatic complexity and breaking the
\emph{Write Simple Units of Code} guideline which resulted in a negative impact on the
OpenSSL maintainability.

@@

\begin{framed}
\textit{\textbf{RQ1} What is the impact of security refactorings on the
maintainability of open-source software?}
\end{framed}
\vspace{-0.1cm}

@@

\begin{framed}
\textit{\textbf{RQ2} Which patterns of security refactorings are more likely to
affect open-source software maintainability?}
\end{framed}
\vspace{-0.1cm}
% here
There are security flaws that are more difficult to refactor than others. For
instance, implementing secure authentication is not as easy as fixing a
cross-site scripting vulnerability since usually the last one can be fixed
without adding new lines of code. A typical fix for the cross-site scripting
vulnerability is presented in Listing~\ref{lst:fix}. The developer added the
function \texttt{htmlentities} to \textit{escape} the data given by the variable
\texttt{\$\_['file']}. Knowing which patterns are more likely to increase
maintainability issues is one step forward to bring awareness to security
engineers of what patterns need more attention. The taxonomy of security
patterns used to answer this question is the same as the one provided by the
authors of the dataset~\cite{Reis:2017:IJSSE}. Maintainability is measured
separately for each pattern.\\

@@

\begin{framed}
\textit{\textbf{RQ1} What is the impact of security refactorings on the
maintainability of open-source software?}
\vspace{-0.05cm}
\end{framed}
\vspace{-0.1cm}

@@

\begin{framed}
\textit{\textbf{RQ2} Which patterns of security refactorings are more likely to
affect open-source software maintainability?}
\vspace{-0.05cm}
\end{framed}
\vspace{-0.1cm}

@@

\begin{framed}
\textit{\textbf{RQ2} Which patterns of security refactorings are more likely to
affect open-source software maintainability?}
\vspace{-0.05cm}
\end{framed}
\vspace{-0.05cm}

@@

The security refactorings dataset provided by the previous
work~\cite{Reis:2017:IJSSE} was collected based on the messages of GitHub
commits produced by project developers to classify the changes performed by them
to fix security flaws. This approach discards security refactorings that were
not explicit in commits messages. Baseline commits are retrieved randomly by selecting one commit from the same
project of a given security refactoring. This approach softens the differences
that may result from the characteristics of each project. However,
maintainability may still be affected by the developers' experience, coding
style and software contribution policies which is not evaluated in this study.
Furthermore, this evaluation considers that $607$ regular commits are enough to
alleviate random irregularities in the maintainability differences of the
baseline.

@@

Researchers investigated the relationship between design patterns and software
maintainability~\cite{10.1007/978-3-642-35267-6-18}. $300$ revisions of
\texttt{JHotDraw} were analyzed to conclude that every introduced pattern
instance improved software maintainability. However, other studies show that the
use of design patterns may introduce maintainability issues into
software~\cite{4493325}. Yskout et. al were not able to detect if the usage of design patterns has a positive impact, but concludes that developers prefer to work with the support of security patterns~\cite{8077802}. The present work studies how security patterns influence maintainability for open-source software.

@@

\noindent
We thank the Software Improvement Group (SIG) team for all the support and
help in validating the methodology.
%ack pedro adao when accepted.
\pagebreak
\balance
